### 2023-12-24 sections/4-results.tex
lfd results for glove

@@

>>>>

% These are going to be boring; saving the interesting discussion for the discussion section

@@

Figure~\ref{fig:results:glove-25-lfd} shows the local fractal dimension by depth for the glove-25 dataset. 
Relative to fashion-mnist, percentile lines for glove-25 are flatter and lower, indicating that the LFD is lower across the entire dataset, and that the LFD does not vary as much by depth.
The 95th percentile of LFD is less than 4 for all depths, and the 50th percentile is less than 2 for all depths. 
Before depth 25, the 95th percentile hovers near 2, and from depth 20 onward, it hovers near 3.5 before dipping sharply at the maximum depths. 
The 50th percentile hovers near 1.5 for all depths.
